Effects of pulsed hollow electron lens operation on the beam core in HL-LHC: \\First experimental studies and simulations.

### 2018-01-29 resex.tex
finished random excitation and damper part

	\caption{\label{fig:10thexpprof} Vertical beam profiles measured with the Beam Synchrotron Radiation Telescope (BSRT) during the 2016 experiments. The profiles are taken at the end of the $10^{\mathrm{th}}$~turn pulsing in V. The black line in the plot of the residual is the current profile minus the profile before applying the excitation and is a measure for the overall change of the distribution. The red line is the current profile minus its Gaussian fit, which gives and indication for the deviation of the distribution from a Gaussian distribution. For details on the analysis see \cite{bsrtprofinj}. The distribution of the reference bunch (left), here slot 50, stays unchanged, while the bunch experiencing the maximum excitation (right), here slot 1300, clearly shows a change to a non-Gaussian distribution.}

@@

\begin{figure}[h]
	%	\begin{minipage}[t]{0.49\linewidth}
	%		\centering
	%		2016 experiment
	%		\includegraphics[width=1.0\linewidth]{2016_bunch_intensity_h7th_no_damper_avg.png}
	%	\end{minipage}	
	%	\begin{minipage}[t]{0.49\linewidth}
	%		\centering
	%		2017 experiment
	%		\includegraphics[width=1.0\linewidth]{2017_bunch_intensity_hv7th_no_damper_avg.png}
	%	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		2016 experiment, $7^\mathrm{th}$ H	\includegraphics[width=1.0\linewidth]{2016_emith_avg_rel_h7th_no_damper.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		2017 experiment, $7^\mathrm{th}$ H+V
		\includegraphics[width=1.0\linewidth]{2017_emith_avg_rel_hv7th_no_damper.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2016_emitv_avg_rel_h7th_no_damper.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017_emitv_avg_rel_hv7th_no_damper.png}
	\end{minipage}	
	\caption{\label{fig:7thexp} Relative horizontal (top) and vertical (bottom) emittance obtained during the 2016 experiments (left) and the 2017 experiment (right) averaged over the bunches experiencing the same excitation amplitude.}
\end{figure}
Similar changes of the emittance are also experimentally observed as shown in Fig.~\ref{fig:7thexp}, where emittance growth was observed only in the horizontal plane for 2016 for pulsing in H, and only in the vertical plane for 2017 for pulsing in V and H+V (for pulsing in H no emittance growth is observed). Just as for the $10^{\mathrm{th}}$~turn pulsing (Fig.~\ref{fig:10thexp}), the emittance growth can be divided also for the $7^{\mathrm{th}}$~turn pulsing in a phase of fast adjustment of the beam distribution and the reach of a new equilibrium state (Fig.~\ref{fig:7thexp}). Also in this case, the distribution changes are also directly visible on the beam profiles measured with the BSRT (Fig.~\ref{fig:7thexpprof}).
\begin{figure}[h]
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		reference bunch,\\ no excitation
		\includegraphics[width=1.0\linewidth]{profile_v_7thhv_slot_2862.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		excited bunch,\\ $7^{\mathrm{th}}$~turn H+V		\includegraphics[width=1.0\linewidth]{profile_v_7thhv_slot_2696.png}
	\end{minipage}
	\caption{\label{fig:7thexpprof} Vertical beam profiles measured with the Beam Synchrotron Radiation Telescope (BSRT) during the 2017 experiments. The profiles are taken at the end of the $7^{\mathrm{th}}$~turn pulsing in H+V. The distribution changes in the reference bunch (left), here slot 2862, are much less than for the bunch experiencing the maximum excitation (right), here slot 2696.}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=1.0\linewidth]{2017_scale_amp_8hv_lbllong.png}
	\caption{\label{fig:8thexploss} Comparison of scaling of loss rates with excitation amplitude for $8^{\mathrm{th}}$~turn pulsing in H+V measured during the 2017 experiment. The excitation amplitude error is 15\% indicated by the horizontal error bars.}
\end{figure}
The only small effect on the beam expected from simulations could then be also confirmed experimentally during the 2017 experiments. For this purpose the excitation amplitude was increased to 96~nrad, which is the maximum kick strength reachable with the transverse damper at injection without risking saturation. As depicted in Fig.~\ref{fig:8thexploss}, the loss rate increased slightly with the excitation amplitude for an excitation in H+V. For an excitation only in V or only in H, no statistically relevant increase was observed. In addition, the beam distribution also changed in the horizontal plane for an excitation only in H as visible in the BSRT profiles Fig.~\ref{fig:8thexpprof} indicating an increase at around $2.0~\sigma$ simultaneously with a depletion of the beam core. For an excitation in H+V the emittances of the references bunches were much smaller, around $1.8~\mu$m normalized emittance on average, than the one of the excited bunches ranging from $2.3~\mu$m to $3.0~\mu$m \cite{resexmd2017}. The references bunches thus experienced a stronger emittance growth due to intra-beam scattering than the excited bunches due to the excitation on top of their smaller emittance growth due to intra-beam scattering. 
\begin{figure}[h]
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		reference bunch,\\ no excitation
		\includegraphics[width=1.0\linewidth]{profile_h_8thh_slot_804.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		excited bunch,\\ $8^{\mathrm{th}}$~turn H	\includegraphics[width=1.0\linewidth]{profile_h_8thh_slot_632.png}
	\end{minipage}
	\caption{\label{fig:8thexpprof} Horizontal beam profiles measured with the Beam Synchrotron Radiation Telescope (BSRT) during the 2017 experiments. The profiles are taken at the end of the $8^{\mathrm{th}}$~turn pulsing in H. The distribution changes in the reference bunch (left), here slot 804, are much less than for the bunch experiencing the maximum excitation (right), here slot 632.}
\end{figure}

@@

Qualitatively, this behavior could be also confirmed experimentally during the 2017 experiments and as example the emittances are depicted in Fig.~\ref{fig:ranexp} for pulsing in V and in H+V, showing no emittance growth in the horizontal for an excitation only in V and emittance growth in both planes for an excitation in H+V. All emittance growth rates are in a comparable range. Note that despite the large emittance growth, the growth rate stays constant and there is no fast adjustment phase succeeded by a new equilibrium state as was the case for the $7^{\mathrm{th}}$ and $10^{\mathrm{th}}$~turn pulsing.
\begin{figure}[h]
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		random excitation V
		\includegraphics[width=1.0\linewidth]{2017_bunch_intensity_vran_no_damper_avg.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		random excitation H+V
		\includegraphics[width=1.0\linewidth]{2017_bunch_intensity_hvran_no_damper_avg.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017_emith_avg_rel_vran_no_damper.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017_emith_avg_rel_hvran_no_damper.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017_emitv_avg_rel_vran_no_damper.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017_emitv_avg_rel_hvran_no_damper.png}
	\end{minipage}	
	\caption{\label{fig:ranexp} Relative intensity (top) and relative horizontal (center) and vertical (bottom) emittance for a random excitation only in V (left) and in H+V (right). Emittance growth is only caused in the plane of excitation.}
\end{figure}
These large changes of the emittance can of course also be seen directly in the BSRT profiles shown in Fig.~\ref{fig:10thexp} for a random excitation only in V.
\begin{figure}[h]
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		reference bunch,\\ no excitation
		\includegraphics[width=1.0\linewidth]{profile_v_7thhv_slot_2862.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		excited bunch,\\ random excitation V		\includegraphics[width=1.0\linewidth]{profile_v_7thhv_slot_2696.png}
	\end{minipage}
	\caption{\label{fig:ranexpprof}\textcolor{red}{update plot} Vertical beam profiles measured with the Beam Synchrotron Radiation Telescope (BSRT) during the 2017 experiments. The profiles are taken at the end of the random excitation in V. The distribution changes in the reference bunch (left), here slot 2862, are much less than for the bunch experiencing the maximum excitation (right), here slot 2696.}
\end{figure}

The experimental results also confirm the small loss predicted in simulations. The losses then suddenly increase for 12~nrad, which is most likely the point when, due to the large emittance increase, the physical aperture starts eating into the more central region of the distribution causing higher losses. Furthermore, the loss rates also add up, meaning that double the loss rate is observed for an excitation in H+V compared to only in H or only V. This is illustrated in  Fig.~\ref{fig:ranexploss}, which also shows the loss rates for the $7^{\mathrm{th}}$~turn pulsing in comparison. Furthermore the loss rate is considerably reduced if the transverse damper is active, which is not the case for the $7^{\mathrm{th}}$~turn pulsing. We will address this subject separately in the next Section, Sec.~\ref{sec:damp}.
\begin{figure}[h]
	\begin{minipage}[t]{0.49\linewidth}
		\centering
	\includegraphics[width=1.0\linewidth]{2017_scale_amp_ranv_lbllong.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017_scale_amp_ranhv_lbllong.png}
	\end{minipage}	
	\caption{\label{fig:ranexploss}  Comparison of scaling of loss rates with excitation amplitude for a random excitation and $7^{\mathrm{th}}$~turn pulsing in V (left) and H+V (right) measured during the 2017 experiment. The excitation amplitude error is 15\% indicated by the horizontal error bars.}
\end{figure}

\subsubsection{Effect of the transverse damper\label{sec:damp}}
For nth turn pulsing no effect. Show example of emittance for 7th turn pulsing and random and refer to Fig.~\ref{fig:ranexploss} for the loss rate.
\begin{figure}[h]
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		random excitation H+V
		\includegraphics[width=1.0\linewidth]{2017_bunch_intensity_hvran_no_damper_avg.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		$7^{\mathrm{th}}$~turn H+V
		\includegraphics[width=1.0\linewidth]{2017_bunch_intensity_hv7th_no_damper_avg.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017_bunch_intensity_hvran_with_damper_avg.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017_bunch_intensity_hv7th_with_damper_avg.png}
	\end{minipage}	
	\caption{\label{fig:damp} Relative intensity for bunches with transverse damper not active (top) and transverse damper active (bottom) for $7^{\mathrm{th}}$~turn pulsing in V (left) and for a random excitation only in V (right).}
\end{figure}

@@

\section{Results of $7^{\mathrm{th}}$~turn pulsing during 2016 and 2017 experiments (additional figures)}
\label{app:sec:simexp:7}

>>>>

	\caption{\label{fig:10thexpprof} Vertical beam profiles measured with the Beam Synchrotron Radiation Telescope (BSRT) during the 2016 experiments. The profiles are taken at the end of the $10^{\mathrm{th}}$~turn pulsing in V. For both bunches the transverse damper is not active. The black line in the plot of the residual is the current profile minus the profile before applying the excitation and is a measure for the overall change of the distribution. The red line is the current profile minus its Gaussian fit, which gives and indication for the deviation of the distribution from a Gaussian distribution. For details on the analysis see \cite{bsrtprofinj}. The distribution of the reference bunch (left), here slot 50, stays unchanged, while the bunch experiencing the maximum excitation (right), here slot 1300, clearly shows a change to a non-Gaussian distribution.}

@@

\begin{figure}[h]
	%	\begin{minipage}[t]{0.49\linewidth}
	%		\centering
	%		2016 experiment
	%		\includegraphics[width=1.0\linewidth]{2016_bunch_intensity_h7th_no_damper_avg.png}
	%	\end{minipage}	
	%	\begin{minipage}[t]{0.49\linewidth}
	%		\centering
	%		2017 experiment
	%		\includegraphics[width=1.0\linewidth]{2017_bunch_intensity_hv7th_no_damper_avg.png}
	%	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		2016 experiment, $7^\mathrm{th}$ H	\includegraphics[width=1.0\linewidth]{2016_emith_avg_rel_h7th_no_damper.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		2017 experiment, $7^\mathrm{th}$ H+V
		\includegraphics[width=1.0\linewidth]{2017_emith_avg_rel_hv7th_no_damper.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2016_emitv_avg_rel_h7th_no_damper.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017_emitv_avg_rel_hv7th_no_damper.png}
	\end{minipage}	
	\caption{\label{fig:7thexp} Relative horizontal (top) and vertical (bottom) emittance obtained during the 2016 experiments (left) and the 2017 experiment (right) averaged over the bunches experiencing the same excitation amplitude.}
\end{figure}
Similar changes of the emittance are also experimentally observed as shown in Fig.~\ref{fig:7thexp}, where emittance growth was observed only in the horizontal plane for 2016 for pulsing in H, and only in the vertical plane for 2017 for pulsing in V and H+V (for pulsing in H no emittance growth is observed). Just as for the $10^{\mathrm{th}}$~turn pulsing (Fig.~\ref{fig:10thexp}), the emittance growth can be divided also for the $7^{\mathrm{th}}$~turn pulsing in a phase of fast adjustment of the beam distribution and the reach of a new equilibrium state (Fig.~\ref{fig:7thexp}). Also in this case, the distribution changes are also directly visible on the beam profiles measured with the BSRT (Appendix~\ref{app:sec:bsrtprof}, Fig.~\ref{fig:7thexpprof}).

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=1.0\linewidth]{2017_scale_amp_8hv_lbllong.png}
	\caption{\label{fig:8thexploss} Comparison of scaling of loss rates with excitation amplitude for $8^{\mathrm{th}}$~turn pulsing in H+V measured during the 2017 experiment. The excitation amplitude error is 15\% indicated by the horizontal error bars.}
\end{figure}
The only small effect on the beam expected from simulations could then be also confirmed experimentally during the 2017 experiments. For this purpose the excitation amplitude was increased to 96~nrad, which is the maximum kick strength reachable with the transverse damper at injection without risking saturation. As depicted in Fig.~\ref{fig:8thexploss}, the loss rate increased slightly with the excitation amplitude for an excitation in H+V. For an excitation only in V or only in H, no statistically relevant increase was observed. In addition, the beam distribution also changed in the horizontal plane for an excitation only in H as visible in the BSRT profiles (Appendix~\ref{app:sec:bsrtprof}, Fig.~\ref{fig:8thexpprof}) indicating an increase at around $2.0~\sigma$ simultaneously with a depletion of the beam core. For an excitation in H+V the emittances of the references bunches were much smaller, around $1.8~\mu$m normalized emittance on average, than the one of the excited bunches ranging from $2.3~\mu$m to $3.0~\mu$m \cite{resexmd2017}. The references bunches thus experienced a stronger emittance growth due to intra-beam scattering than the excited bunches due to the excitation on top of their smaller emittance growth due to intra-beam scattering.

@@

Qualitatively, this behavior could be also confirmed experimentally during the 2017 experiments and as example the emittances are depicted in Fig.~\ref{fig:ranexp} for pulsing in V and in H+V, showing no emittance growth in the horizontal for an excitation only in V and emittance growth in both planes for an excitation in H+V. All emittance growth rates are in a comparable range. Note that despite the large emittance growth, the growth rate stays constant and there is no fast adjustment phase succeeded by a new equilibrium state as was the case for the $7^{\mathrm{th}}$ and $10^{\mathrm{th}}$~turn pulsing.
\begin{figure}[h]
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		random excitation V
		\includegraphics[width=1.0\linewidth]{2017_bunch_intensity_vran_no_damper_avg.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		random excitation H+V
		\includegraphics[width=1.0\linewidth]{2017_bunch_intensity_hvran_no_damper_avg.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017_emith_avg_rel_vran_no_damper.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017_emith_avg_rel_hvran_no_damper.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017_emitv_avg_rel_vran_no_damper.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017_emitv_avg_rel_hvran_no_damper.png}
	\end{minipage}	
	\caption{\label{fig:ranexp} Relative intensity (top) and relative horizontal (center) and vertical (bottom) emittance for a random excitation only in V (left) and in H+V (right). Emittance growth is only caused in the plane of excitation.}
\end{figure}
These large changes of the emittance can of course also be seen directly in the BSRT profiles shown in Fig.~\ref{fig:ranexpprof} for a random excitation only in V. In comparison to for example the $10^{\mathrm{th}}$~turn pulsing (Fig.~\ref{fig:10thexpprof}), the distribution also stays Gaussian in case of a random excitation while for the $10^{\mathrm{th}}$~turn pulsing it clearly adopts a non-Gaussian shape.
\begin{figure}[h]
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		reference bunch,\\ no excitation
		\includegraphics[width=1.0\linewidth]{profile_v_ranv_slot_1698.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		excited bunch,\\ random excitation V
		\includegraphics[width=1.0\linewidth]{profile_v_ranv_slot_1532.png}
	\end{minipage}
	\caption{\label{fig:ranexpprof}Vertical beam profiles measured with the Beam Synchrotron Radiation Telescope (BSRT) during the 2017 experiments. The profiles are taken at the end of the random excitation in V. For both bunches the transverse damper is not active. The distribution changes in the reference bunch (left), here slot 1698, are much less than for the bunch experiencing the maximum excitation (right), here slot 2696.}
\end{figure}

The experimental results also confirm the small loss predicted in simulations. The losses then suddenly increase for 12~nrad, which is most likely the point when, due to the large emittance increase, the physical aperture starts eating into the more central region of the distribution causing higher losses. Furthermore, the loss rates also add up, meaning that double the loss rate is observed for an excitation in H+V compared to only in H or only V. This is illustrated in  Fig.~\ref{fig:ranexploss}, which also shows the loss rates for the $7^{\mathrm{th}}$~turn pulsing in comparison. Furthermore the loss rate is considerably reduced if the transverse damper is active, which is not the case for the $7^{\mathrm{th}}$~turn pulsing. We will address this subject separately in the next Section, Sec.~\ref{sec:damp}.
\begin{figure}[h]
	\begin{minipage}[t]{0.49\linewidth}
		\centering
	\includegraphics[width=1.0\linewidth]{2017_scale_amp_ranv_lbllong.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017_scale_amp_ranhv_lbllong.png}
	\end{minipage}	
	\caption{\label{fig:ranexploss}  Comparison of scaling of loss rates with excitation amplitude for a random excitation and $7^{\mathrm{th}}$~turn pulsing in V (left) and H+V (right) measured during the 2017 experiment. The excitation amplitude error is 15\% indicated by the horizontal error bars. Note that for $7^{\mathrm{th}}$~turn pulsing the transverse damper does not influence the loss rate, while for a random excitation the loss rate is considerably reduced for the bunches with transverse damper active.}
\end{figure}

\subsubsection{Effect of the transverse damper\label{sec:damp}}
For all $n^{\mathrm{th}}$~turn pulsing patterns, the transverse damper does not change any of the observables studied during the experiments, explicitly losses, emittance and beam distribution suggesting that indeed it is not capable of damping any resonant excitation. On the other hand, the transverse damper considerably decreases loss rates, emittance growth and distribution changes for the random excitation. As an example, the vertical emittance growth is compared for the $7^{\mathrm{th}}$~turn pulsing in V and a random excitation in V in Fig.~\ref{fig:damp} and the loss rates in Fig.~\ref{fig:ranexploss} illustrating impressively the above behavior. 
For nth turn pulsing no effect. Show example of emittance for 7th turn pulsing and random and refer to Fig.~\ref{fig:ranexploss} for the loss rate.
\begin{figure}[h]
	\centering
	random excitation H+V\\
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		damper not active
		\includegraphics[width=1.0\linewidth]{2017_emitv_avg_rel_vran_no_damper.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		damper active
		\includegraphics[width=1.0\linewidth]{2017_emitv_avg_rel_vran_with_damper.png}
	\end{minipage}	
		\centering
		$7^{\mathrm{th}}$~turn H+V\\
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		damper not active
		\includegraphics[width=1.0\linewidth]{2017_emitv_avg_rel_v7th_no_damper_no_text.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		damper active
		\includegraphics[width=1.0\linewidth]{2017_emitv_avg_rel_v7th_with_damper_no_text.png}
	\end{minipage}	
	\caption{\label{fig:damp} Relative intensity for bunches with transverse damper not active (top) and transverse damper active (bottom) for $7^{\mathrm{th}}$~turn pulsing in V (left) and for a random excitation only in V (right).}
\end{figure}
\textcolor{red}{Any idea why? Daniel, help!}

@@

\section{BSRT profiles for $7^{\mathrm{th}}$ and $8^{\mathrm{th}}$~turn pulsing during 2017 experiments}
\label{app:sec:bsrtprof}
\begin{figure}[h]
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		reference bunch,\\ no excitation
		\includegraphics[width=1.0\linewidth]{profile_v_7thhv_slot_2862.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		excited bunch,\\ $7^{\mathrm{th}}$~turn H+V	
		\includegraphics[width=1.0\linewidth]{profile_v_7thhv_slot_2696.png}
	\end{minipage}
	\caption{\label{fig:7thexpprof} Vertical beam profiles measured with the Beam Synchrotron Radiation Telescope (BSRT) during the 2017 experiments. The profiles are taken at the end of the $7^{\mathrm{th}}$~turn pulsing in H+V. For both bunches the transverse damper is not active. The distribution changes in the reference bunch (left), here slot 2862, are much less than for the bunch experiencing the maximum excitation (right), here slot 2696.}
\end{figure}
\begin{figure}[h]
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		reference bunch,\\ no excitation
		\includegraphics[width=1.0\linewidth]{profile_h_8thh_slot_804.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		excited bunch,\\ $8^{\mathrm{th}}$~turn H
		\includegraphics[width=1.0\linewidth]{profile_h_8thh_slot_632.png}
	\end{minipage}
	\caption{\label{fig:8thexpprof} Horizontal beam profiles measured with the Beam Synchrotron Radiation Telescope (BSRT) during the 2017 experiments. The profiles are taken at the end of the $8^{\mathrm{th}}$~turn pulsing in H. For both bunches the transverse damper is not active. The distribution changes in the reference bunch (left), here slot 804, are much less than for the bunch experiencing the maximum excitation (right), here slot 632.}
\end{figure}
